---
title: "Data Sets for Many-Analyses"
author: "Julia Haaf"
date: "2/28/2020"
output: pdf_document
---

This document takes the original data and subsets it using different exclusion criteria. It is therefore a documentation of all data sets used in the many-analyses.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(metafor)
library(tidyverse)
```

```{r prep-fun, include = F}
analysis <- function(data)
{
  # create statistics after filtering for cases that match index
  location <- data$location[1] #saves first row from location variable
  source <- data$source[1]
  n_tv    <- length(data$pro_minus_anti[data$ms_condition == 'tv']) #n for tv condition
  n_ms    <- length(data$pro_minus_anti[data$ms_condition == 'ms']) #n for ms condition
  sd_tv   <-     sd(data$pro_minus_anti[data$ms_condition == 'tv']) #sd for tv participants at that site
  sd_ms   <-     sd(data$pro_minus_anti[data$ms_condition == 'ms']) #sd for ms participants at that site
  mean_tv <-   mean(data$pro_minus_anti[data$ms_condition == 'tv']) #mean for tv participants at that site
  mean_ms <-   mean(data$pro_minus_anti[data$ms_condition == 'ms']) #mean for ms participants at that site
  expert <- mean(data$expert) #shortcut to indicate whether site is expert or not (0 = inhouse 1 = expert)
  d_diff <- (mean_ms - mean_tv)/ sqrt((sd_ms^2+sd_tv^2)/2) #computes Cohen's D effect size
  nhst <- t.test(data$pro_minus_anti~data$ms_condition)
  t <- nhst$statistic
  df <- nhst$parameter
  p.value <- nhst$p.value
  result <- data.frame(location, source, expert, n_tv, mean_tv, sd_tv, n_ms, mean_ms, sd_ms, d_diff, t, df, p.value) #results to be reported
  result <- escalc(n1i = n_ms, n2i = n_tv, m1i = mean_ms, m2i = mean_tv, 
                           sd1i = sd_ms, sd2i = sd_tv, data = result, measure = "SMD", 
                           append = TRUE)
  result$sei <- sqrt(result$vi)
  return(result)
}

run.analysis <- function(data){
  datl <- split(data, data$source)
  res <- lapply(datl, analysis)
  resm <- do.call(rbind, res)
}
```

sitesource_label = case_when(source == "ufl" ~ "University of Florida",
                                             source == "occid" ~ "Occidental College",
                                             source == "ashland" ~ "Ashland University",
                                             source == "ithaca" ~ "Ithaca College",
                                             source == "riverside" ~ "University of California, Riverside",
                                             source == "wesleyan_inhouse" ~ "Wesleyan University",
                                             source == "uwmadison_expert" ~ "University of Wisconsin",
                                             source == "uwmadison_inhouse" ~ "University of Wisconsin",
                                             source == "vcu" ~ "Virginia Commonwealth University",
                                             source == "sou_inhouse" ~ "Southern Oregon University",
                                             source == "plu" ~ "Pacific Lutheran University",
                                             source == "byui" ~ "Brigham Young University - Idaho",
                                             source == "azusa" ~ "Azusa Pacific University",
                                             source == "cnj" ~ "The College of New Jersey",
                                             source == "wpi" ~ "Worcester Polytechnic Institute",
                                             source == "illinois" ~ "University of Illinois",
                                             source == "kansas_expert" ~ "University of Kansas",
                                             source == "kansas_inhouse" ~ "University of Kansas",
                                             source == "upenn" ~ "University of Pennsylvania",
                                             source == "pace_inhouse" ~ "Pace University",
                                             source == "pace_expert" ~ "Pace University")
  )

```{r data}
merged <- readRDS("data/merged_deidentified_full.rds")

# head(merged)
nrow(merged)

# table(merged$race)
# sum(is.na(merged$race))
# sum(is.na(merged$countryofbirth))

levels(merged$countryofbirth)
merged$usborn <- ifelse(merged$countryofbirth %in% c(1, "united states", "United State", "United States", "United States of America"
                                                     , "us", "US", "usa", "USA", "U.S.A", "U.S."
                                                     , "The United States of America."), 1, 0)

levels(merged$race)
merged$iswhite <- ifelse(merged$race %in% c(1, "White/Caucasian ", "White/Caucasian/Welsh,German,Italian", "white ", "Irish American "
                                            , "1 AND 2", "1 AND 4 AND 5", "1 AND 6", "1,2", "1,2,4", "1,3", "1,3,4", "1,4", "1,4,5"
                                            , "1,4,6", "1,5", "1,6", "white/ native american", "African American and White "
                                            , "Caucasion & Hispanic/Latina", "Thai and Caucasian"), 1, 0)

# Create variables, indexes, and exclusion rules ----
# compute exclusion rules
merged <- mutate(merged, 
                 # Exclusion rule 1:
                 #1. Wrote something for both writing prompts
                 #2. Completed all six items evaluating the essay authors)
                 pass_ER1 = !is.na(pro_minus_anti) & (msincomplete == 0 | is.na(msincomplete)) & # completed both prompts
                   !is.na(prous3) & !is.na(prous4) & !is.na(prous5) &  # P provided all 3 ratings of pro-us essay
                   !is.na(antius3) & !is.na(antius4) & !is.na(antius5),# P provided all 3 ratings of anti-us
                 # Exclusion rule 2:
                 # as above, plus
                 #3. Identify as White (race == 1)
                 #4. Born in USA (countryofbirth == 1)
                 pass_ER2 = pass_ER1 &
                   (iswhite == 1) & # white ps, NA race discarded
                   (usborn == 1),
                 # Exclusion rule 3:
                 # as above, plus
                 # 5. Score a 7 or higher on the American Identity item
                 pass_ER3 = pass_ER2 &
                   (americanid >= 7 & !is.na(americanid)) # strongly ID as american, NAs discarded
)
```

## Exclusion Criteria

Person-level exclusion (Taken from Klein et al., 2019):

1. All participants who did not complete the materials.
2. 1 + All participants who do not identify as white and who were born outside of the United States.
3. 2 + All participants who responded lower than 7 on an American Identity item.

Study-level exclusion based on $N$ (from the preregistration):

1. No study-level exclusion.
2. All studies that have less than 60 participants collected.
3. All studies that habe less than 40 participants per cell.

Study-level exclusion based on expert advise (from the comment):

1. No exclusion based on expert advise.
2. In-house studies are excluded.

All exclusion criteria are crossed in the following way:

```{r}
person.ex <- 1:3
n.ex <- 1:3
expert.ex <- 1:2

crit <- expand.grid(person.ex, n.ex, expert.ex)
nrow(crit)
```


## Original Analysis

We aim at reanalyzing the key findings of Klein et al (2019) using the exclusion settings (1,1,1), (2,1,1), and (3,1,1).

```{r data-111, fig.width=6, fig.height=4}
merged.111 <- subset(merged, pass_ER1 == TRUE)
nrow(merged.111)

#write data
write.csv2(merged.111, "data/reanalysis_111.csv", row.names = FALSE)
metaset.111 <- run.analysis(merged.111)
write.csv2(metaset.111, "data/metaset_111.csv", row.names = FALSE)
```

```{r data-211, fig.width=6, fig.height=4}
merged.211 <- subset(merged, pass_ER2 == TRUE)
nrow(merged.211)

#write data
write.csv2(merged.211, "data/reanalysis_211.csv", row.names = FALSE)
metaset.211 <- run.analysis(merged.211)
write.csv2(metaset.211, "data/metaset_211.csv", row.names = FALSE)
```

```{r data-311, fig.width=6, fig.height=4}
merged.311 <- subset(merged, pass_ER3 == TRUE)
nrow(merged.311)

#write data
write.csv2(merged.311, "data/reanalysis_311.csv", row.names = FALSE)
metaset.311 <- run.analysis(merged.311)
write.csv2(metaset.311, "data/metaset_311.csv", row.names = FALSE)
```

## Analysis for the Main Claim of the Comment

We aim at reanalyzing the main claim of Chatard et al (2020) using the exclusion settings (1,3,2), (2,3,2), and (3,3,2). Note that the study-level exclusions are based on the number of participants for exclusion criterion 1.

```{r data-132}
nbysourcebycond <- with(merged.111, tapply(dv_order, list(source, ms_condition), length))
include3 <- names(which(rowSums(nbysourcebycond >= 40) ==2))

merged.132 <- subset(merged.111, source %in% include3 & expert == 1)
nrow(merged.132)

write.csv2(merged.132, "data/reanalysis_132.csv", row.names = FALSE)
metaset.132 <- run.analysis(merged.132)
write.csv2(metaset.132, "data/metaset_132.csv", row.names = FALSE)
```

```{r data-232}
merged.232 <- subset(merged.211, source %in% include3 & expert == 1)
nrow(merged.232)

write.csv2(merged.232, "data/reanalysis_232.csv", row.names = FALSE)
metaset.232 <- run.analysis(merged.232)
write.csv2(metaset.232, "data/metaset_232.csv", row.names = FALSE)
```

```{r data-332}
merged.332 <- subset(merged.311, source %in% include3 & expert == 1)
nrow(merged.332)

write.csv2(merged.332, "data/reanalysis_332.csv", row.names = FALSE)
metaset.332 <- run.analysis(merged.332)
write.csv2(metaset.332, "data/metaset_332.csv", row.names = FALSE)
```

```{r check-meta}
metafor::rma(metaset.332$d_diff, sei = metaset.332$sei, method="FE")
```

## All Other Variants

### Exclusion .1.2

```{r data-112}
merged.112 <- subset(merged.111, expert == 1)
nrow(merged.112)

write.csv2(merged.112, "data/reanalysis_112.csv", row.names = FALSE)
metaset.112 <- run.analysis(merged.112)
write.csv2(metaset.112, "data/metaset_112.csv", row.names = FALSE)
```

```{r data-212}
merged.212 <- subset(merged.211, expert == 1)
nrow(merged.212)

write.csv2(merged.212, "data/reanalysis_212.csv", row.names = FALSE)
metaset.212 <- run.analysis(merged.212)
write.csv2(metaset.212, "data/metaset_212.csv", row.names = FALSE)
```

```{r data-312}
merged.312 <- subset(merged.311, expert == 1)
nrow(merged.312)

write.csv2(merged.312, "data/reanalysis_312.csv", row.names = FALSE)
metaset.312 <- run.analysis(merged.312)
write.csv2(metaset.312, "data/metaset_312.csv", row.names = FALSE)
```

### Exclusion .2.1

```{r data-121}
nbysource <- with(merged.111, tapply(dv_order, source, length))
include2 <- names(which(nbysource > 60))

merged.121 <- subset(merged.111, source %in% include2)
nrow(merged.121)

write.csv2(merged.121, "data/reanalysis_121.csv", row.names = FALSE)
metaset.121 <- run.analysis(merged.121)
write.csv2(merged.121, "data/metaset_121.csv", row.names = FALSE)
```

```{r data-221}
merged.221 <- subset(merged.211, source %in% include2)
nrow(merged.212)

write.csv2(merged.221, "data/reanalysis_221.csv", row.names = FALSE)
metaset.221 <- run.analysis(merged.221)
write.csv2(merged.221, "data/metaset_221.csv", row.names = FALSE)
```

```{r data-321}
merged.321 <- subset(merged.311, source %in% include2)
nrow(merged.321)

write.csv2(merged.321, "data/reanalysis_321.csv", row.names = FALSE)
metaset.321 <- run.analysis(merged.321)
write.csv2(metaset.321, "data/metaset_321.csv", row.names = FALSE)
```

### Exclusion .2.2

```{r data-122}
merged.122 <- subset(merged.111, source %in% include2 & expert == 1)
nrow(merged.122)

write.csv2(merged.122, "data/reanalysis_122.csv", row.names = FALSE)
metaset.122 <- run.analysis(merged.122)
write.csv2(merged.122, "data/metaset_122.csv", row.names = FALSE)
```

```{r data-222}
merged.222 <- subset(merged.211, source %in% include2 & expert == 1)
nrow(merged.222)

write.csv2(merged.222, "data/reanalysis_222.csv", row.names = FALSE)
metaset.222 <- run.analysis(merged.222)
write.csv2(merged.222, "data/metaset_222.csv", row.names = FALSE)
```

```{r data-322}
merged.322 <- subset(merged.311, source %in% include2 & expert == 1)
nrow(merged.322)

write.csv2(merged.322, "data/reanalysis_322.csv", row.names = FALSE)
metaset.322 <- run.analysis(merged.322)
write.csv2(metaset.322, "data/metaset_322.csv", row.names = FALSE)
```

### Exclusion .3.1


```{r data-131}
merged.131 <- subset(merged.111, source %in% include3)
nrow(merged.131)

write.csv2(merged.131, "data/reanalysis_131.csv", row.names = FALSE)
merged.131 <- run.analysis(merged.131)
write.csv2(metaset.132, "data/metaset_131.csv", row.names = FALSE)
```

```{r data-231}
merged.231 <- subset(merged.211, source %in% include3)
nrow(merged.231)

write.csv2(merged.231, "data/reanalysis_231.csv", row.names = FALSE)
metaset.231 <- run.analysis(merged.231)
write.csv2(metaset.231, "data/metaset_231.csv", row.names = FALSE)
```

```{r data-331}
merged.331 <- subset(merged.311, source %in% include3 & expert == 1)
nrow(merged.331)

write.csv2(merged.331, "data/reanalysis_331.csv", row.names = FALSE)
metaset.331 <- run.analysis(merged.331)
write.csv2(metaset.331, "data/metaset_331.csv", row.names = FALSE)
```